Automatic Matching of Bullet Lands

### 2016-01-16 imaging-paper.Rnw
AUC calculation upped to 10,000 samples - still a tie between ccf and S

aucs <- plyr::ldply(features, function(x) {
  subbstats <- subset(bstats, flagged == FALSE)
  pos.scores <- sample(subbstats[which(subbstats$match),x], 5000, replace=TRUE)
  neg.scores <- sample(subbstats[which(!subbstats$match),x], 5000, replace=TRUE)
  data.frame(x, upper=mean(pos.scores > neg.scores), 
             lower = mean(pos.scores < neg.scores))
})
aucs <- melt(aucs, measure.var=c("lower", "upper"))
names(aucs) <- c("variable", "type", "auc")
rocs <- merge(rocs, aucs, by=c("variable", "type"))
rocs$variable <- reorder(rocs$variable, -rocs$auc, min)
levels(rocs$variable)[3:4] <- c("#non-matches", "#matches")

>>>>

set.seed(20140501)
aucs <- plyr::ldply(features, function(x) {
  subbstats <- subset(bstats, flagged == FALSE)
  pos.scores <- sample(subbstats[which(subbstats$match),x], 10000, replace=TRUE)
  neg.scores <- sample(subbstats[which(!subbstats$match),x], 10000, replace=TRUE)
  data.frame(x, upper=mean(pos.scores > neg.scores), 
             lower = mean(pos.scores < neg.scores))
})
aucs <- melt(aucs, measure.var=c("lower", "upper"))
names(aucs) <- c("variable", "type", "auc")
rocs <- merge(rocs, aucs, by=c("variable", "type"))
rocs$variable <- reorder(rocs$variable, -rocs$auc, min)
levels(rocs$variable)[3:4] <- c("#non-matches", "#matches")
